Prop off

### 2021-02-17 analysis/rev_prototyping/prop_off_prelim_results.Rmd
change pipeline structure

all_di <- read.csv(here::here("miscabund_di.csv"))

@@

```
```{r}

ggplot(all_di, aes(prop_off_sim_95, mean_prop_off_actual, color = log(nparts))) +
  geom_point() +
  geom_line(aes(prop_off_sim_95, prop_off_sim_95))

all_di %>%
  group_by(singletons) %>%
  summarize(prop_off_m = mean(prop_off_sig_mean),
            prop_off_f = mean(prop_off_sig_5pc))

all_di %>%
  filter(prop_off_sig_mean) %>%
  group_by(singletons) %>%
  summarize(diff = mean(mean_prop_off_actual - mean_prop_off_sim))

ggplot(all_di, aes(nparts, prop_off_sim_95_1t)) +
  geom_point() +
  scale_x_log10()

ggplot(all_di, aes(nparts, prop_off_sim_95_1t)) +
  geom_point() +
  scale_x_log10() +
  xlim(0, 10000)

@@

### One where both are significant

```{r}
di_10 <- read.csv(here::here("misc_10_di.csv"))
diffs_10 <- read.csv(here::here("misc_10_diffs.csv"))

po_10 <- data.frame(
  actual = di_10$prop_off_actual[1:nrow(diffs_10)],
  sim = diffs_10$prop_off
)

po_long_10 <- po_10%>%
  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")

ggplot(po_long_10, aes(prop_off, color = source)) +
  geom_density()

filter(di_10, source == "observed") %>%
  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)

ecdfs_10 <- data.frame(
  actual = ecdf(po_10$actual)(seq(0, 1, length.out = 100)),
  sim = ecdf(po_10$sim)(seq(0, 1, length.out = 100)),
  val = seq(0, 1, length.out = 100)
) %>%
  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")

ggplot(ecdfs_10, aes(val, ecdf, color = source)) +
  geom_line()

ks.test(po_10$actual, po_10$sim, alternative = "less")
t.test(po_10$actual, po_10$sim)

glm_10 <- (glm(prop_off ~ source, data = po_long_10, family = Gamma))

summary(glm_10)

predict(glm_10, newdata = data.frame(source = c('actual', 'sim')), type = "response")

@@

### One where mean is and 95 is not

```{r}
di_11 <- read.csv(here::here("misc_11_di.csv"))
diffs_11 <- read.csv(here::here("misc_11_diffs.csv"))

po_11 <- data.frame(
  actual = di_11$prop_off_actual[1:nrow(diffs_11)],
  sim = diffs_11$prop_off
)

po_long_11 <- po_11%>%
  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")

ggplot(po_long_11, aes(prop_off, color = source)) +
  geom_density()

filter(di_11, source == "observed") %>%
  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)

ecdfs_11 <- data.frame(
  actual = ecdf(po_11$actual)(seq(0, 1, length.out = 100)),
  sim = ecdf(po_11$sim)(seq(0, 1, length.out = 100)),
  val = seq(0, 1, length.out = 100)
) %>%
  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")

ggplot(ecdfs_11, aes(val, ecdf, color = source)) +
  geom_line()

ks.test(po_11$actual, po_11$sim, alternative = "less")
t.test(po_11$actual, po_11$sim)

glm_11 <- (glm(prop_off ~ source, data = po_long_11, family = Gamma))

summary(glm_11)

predict(glm_11, newdata = data.frame(source = c('actual', 'sim')), type = "response")

### One where neither is

```{r}
di_22 <- read.csv(here::here("misc_22_di.csv"))
diffs_22 <- read.csv(here::here("misc_22_diffs.csv"))

po_22 <- data.frame(
  actual = di_22$prop_off_actual[1:nrow(diffs_22)],
  sim = diffs_22$prop_off
)

po_long_22 <- po_22%>%
  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")

ggplot(po_long_22, aes(prop_off, color = source)) +
  geom_density()

filter(di_22, source == "observed") %>%
  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)

ecdfs_22 <- data.frame(
  actual = ecdf(po_22$actual)(seq(0, 1, length.out = 100)),
  sim = ecdf(po_22$sim)(seq(0, 1, length.out = 100)),
  val = seq(0, 1, length.out = 100)
) %>%
  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")

ggplot(ecdfs_22, aes(val, ecdf, color = source)) +
  geom_line()

ks.test(po_22$actual, po_22$sim, alternative = "less")

t.test(po_22$actual, po_22$sim)

glm_22 <- (glm(prop_off ~ source, data = po_long_22, family = Gamma))

summary(glm_22)

predict(glm_22, newdata = data.frame(source = c('actual', 'sim')), type = "response")

The KS test finds even very small differences. Ditto t tests and Wilcox and GLMs.

Is it valid to compare the **mean** of the actual to the **95%** of the sims? I raise this because comparing the 5% to the 95% seems awfully conservative. But I'm not sure.

>>>>

all_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_di.csv"))

@@

@@

```{r}

ggplot(filter(all_di, n_po_comparisons > 20), aes(mean_po_comparison_percentile)) +
  geom_histogram() +
  facet_wrap(vars(singletons), scales = "free_y")

ggplot(filter(all_di, n_po_comparisons > 20), aes(n_po_comparisons)) +
  geom_histogram()

all_di %>% group_by(singletons) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))

ggplot(all_di, aes(mean_po_comparison_95, mean_po_comparison, color = log(nparts))) +
  geom_point() +
  geom_line(aes(mean_po_comparison_95, mean_po_comparison_95))

all_di %>%
  filter(mean_po_comparison_percentile > 95) %>%
  group_by(singletons) %>%
  summarize(diff = mean(mean_po_comparison - mean_po_comparison_95))

ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t)) +
  geom_point() +
  scale_x_log10()

ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t)) +
  geom_point() +
  scale_x_log10() +
  xlim(0, 10000)

@@
